---
title: "ZZ R md presentation"
author: "zz"
date: "15 May 2019"
output:
  ioslides_presentation: default
  slidy_presentation: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```
## My new slide
Something here

***
Slide no title

## my title

### a top level


- bule 1

- bule 2

          1. item 1
          2. Item 2

*italika*

**debelo**

## for

'for (i %in% 1:10) i'
```{r, comment = "", echo=FALSE}
head(mtcars)
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

